---
title: "Analysis Group 6"
author: "Rebecca Scarratt"
date: "2023-07-29"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Again, we start by loading the data, setting the working directory and loading in the pre-processed data.

```{r load packages, working directory and data}
# we load the packages
library(dplyr)
library(ggplot2)
library(tidyverse)

# Set seed for reproducability
set.seed(1)

# set working directory
setwd("C:/Users/au672599/OneDrive - Aarhus Universitet/Documents/PhD Rebecca/Summer School/Online studies data")

# load in the data file. Note this only works with a .csv file. Here you need to change the name of the file.

data <- read.csv('survey_data_group6.csv')
data$X <- NULL

# if it worked correctly, you should now see the dataframe 'data' appear in the Environment panel. You can click on it, to open it and check that it looks like your messy data file.
```

## Descriptive Statistics

First, let's start by looking at the data.
How many respondents do we have?
What is the distribution of familiarity?
What is the distribution of valence?

```{r descriptive statistics}

print(length(unique(data$run_id)))
# whatever outputs here is the number of respondents

# describe the valence
print(summary(data$valence))
plot(density(data$valence))

# describe the familiarity
data$familiarity <- as.factor(data$familiarity)
print(summary(data$familiarity))

```


## ploting

```{r plotting}
# examples of plots

ggplot(data, aes(x=song, y=valence ))+
geom_boxplot()+
  labs(title = 'Valence per song')

ggplot(data, aes(x=type, y=valence ))+
geom_boxplot()+
  labs(title = 'Valence per type')

ggplot(data, aes(x=song, y=valence, fill = type))+
geom_boxplot()+
  labs(title = 'Valence per type and song')

```

## Inferential statistics

This is where we want to do statistics to see if there are any significant differences between each song and between each intrumental and lyric song.
