---
title: "Analysis Group 2"
author: "Rebecca Scarratt"
date: "2023-07-29"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Again, we start by loading the data, setting the working directory and loading in the pre-processed data.

```{r load packages, working directory and data}
# we load the packages
library(dplyr)
library(ggplot2)
library(tidyverse)

# Set seed for reproducability
set.seed(1)

# set working directory
setwd("C:/Users/au672599/OneDrive - Aarhus Universitet/Documents/PhD Rebecca/Summer School/Online studies data")

# load in the data file. Note this only works with a .csv file. Here you need to change the name of the file.

data <- read.csv('survey_data_group2.csv')
data$X <- NULL

# if it worked correctly, you should now see the dataframe 'data' appear in the Environment panel. You can click on it, to open it and check that it looks like your messy data file.
```

## Descriptive Statistics

First, let's start by looking at the data.
How many respondents do we have?
What is the distribution of musical Exeprtise?
What si the average response per rhythmic complexity?

```{r descriptive statistics}

print(length(unique(data$run_id)))
# whatever outputs here is the number of respondents

# describe the responses for high complexity
print(summary(data$high))
plot(density(data$high))

# describe the responses for mid complexity
print(summary(data$medium))
plot(density(data$medium))

# describe the responses for low complexity
print(summary(data$low))
plot(density(data$low))

# distribution of musical expertise
print(summary(data$musical_expertise))
data$musical_expertise <- as.factor(data$musical_expertise)
print(summary(data$musical_expertise))
# it's up to you to interpret what these numbers mean
```


## ploting

```{r plotting}
# because we need the data non pivoted, let's load in the other data format we had
no_pivot <- read.csv('survey_data_group2_nonpivoted.csv')

no_pivot$complexity <- factor(no_pivot$complexity, levels = c("low", "medium", "high"))

no_pivot$musical_expertise <- factor(no_pivot$musical_expertise)

ggplot(no_pivot, aes(x=complexity, y=response ))+
geom_boxplot()+
  labs(title = 'Enjoyment per complexity')

ggplot(no_pivot, aes(x=complexity, y=response, fill = musical_expertise))+
geom_boxplot()+
  labs(title = 'Enjoyment per complexity')

```

## Inferential statistics

This is where we want to do statistics to see if there are any significant differences between each rhythmic complexity, and then whether the enjoyment in each complexity changes with the self-rated musical expertise
