---
title: "Analysis Group 5"
author: "Rebecca Scarratt"
date: "2023-07-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Again, we start by loading the data, setting the working directory and loading in the pre-processed data.

```{r load packages, working directory and data}
# we load the packages
library(dplyr)
library(ggplot2)
library(tidyverse)

# Set seed for reproducability
set.seed(1)

# set working directory
setwd("C:/Users/au672599/OneDrive - Aarhus Universitet/Documents/PhD Rebecca/Summer School/Online studies data")

# load in the data file. Note this only works with a .csv file. Here you need to change the name of the file.

data <- read.csv('survey_data_group5.csv')
data$X <- NULL

# if it worked correctly, you should now see the dataframe 'data' appear in the Environment panel. You can click on it, to open it and check that it looks like your messy data file.
```


## Descriptive Statistics

First, let's start by looking at the data. How many respondents do we have?
What distribution of responses per emotion? 
What distribution of responses per motivation? 


```{r descriptive statistics}

print(length(unique(data$run_id)))
# whatever outputs here is the number of respondents

# distribution of responses per emotion
data$task <- factor(data$task)
response_per_emotion <- data %>%
  group_by(task) %>% 
  summarise(mean = mean(response),
            sd = sd(response),
            max = max(response),
            min = min(response))

# responses per motivation
# here I only added the means, but you could also add max, min and sd of each
response_per_motivation <- data %>%
  filter(!is.na(personal.entertainment), !is.na(discharge), !is.na(personal.revival),
         !is.na(strong.sensation), !is.na(personal.diversion), !is.na(mental.working)) %>% 
  group_by(task) %>% 
  summarise(mean_entertainment = mean(personal.entertainment),
            mean_discharge = mean(discharge),
            mean_revival = mean(personal.revival),
            mean_sensation = mean(strong.sensation),
            mean_diversion = mean(personal.diversion),
            mean_mental = mean(mental.working))


```

## ploting

```{r plotting}

ggplot(data, aes(x=task, y=response ))+
geom_boxplot()+
  labs(title = 'Response per emotion')

# to do some other ploting, we need to modify the format of the data
data_pivot <- data %>%pivot_longer(!c(run_id, task, response), names_to = 'motivation', values_to = 'rating' )

data_pivot %>% filter(!is.na(rating)) %>% 
  ggplot(aes(x=motivation, y=rating ))+
geom_boxplot()+
  labs(title = 'Rating per motivation')

# how does this differ per emotion
data_pivot %>% filter(!is.na(rating)) %>% 
  ggplot(aes(x=motivation, y=rating ))+
geom_boxplot()+
  labs(title = 'Rating per motivation')+
  facet_wrap(~task)

# how does this differ per emotion
data_pivot %>% filter(!is.na(rating)) %>% 
  ggplot(aes(x=motivation, y=rating, fill =task))+
geom_boxplot()+
  labs(title = 'Rating per motivation')+
  facet_wrap(~task)

# how does this differ per emotion - different way of plotting
data_pivot %>% filter(!is.na(rating)) %>% 
  ggplot(aes(x=motivation, y=rating, fill =task))+
geom_boxplot()+
  labs(title = 'Rating per motivation')

```

## Inferential statistics

This is where we want to do statistics to see if there are any significant differences between each of these conditions.