---
title: "Analysis Group 1"
author: "Rebecca Scarratt"
date: "2023-07-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Again, we start by loading the data, setting the working directory and loading in the pre-processed data.

```{r load packages, working directory and data}
# we load the packages
library(dplyr)
library(ggplot2)
library(tidyverse)

# Set seed for reproducability
set.seed(1)

# set working directory
setwd("C:/Users/au672599/OneDrive - Aarhus Universitet/Documents/PhD Rebecca/Summer School/Online studies data")

# load in the data file. Note this only works with a .csv file. Here you need to change the name of the file.

data <- read.csv('survey_data_group1.csv')
data$X <- NULL

# if it worked correctly, you should now see the dataframe 'data' appear in the Environment panel. You can click on it, to open it and check that it looks like your messy data file.
```


## Descriptive Statistics

First, let's start by looking at the data. How many respondents do we have?
What is the average number of total items, correct items and incorrect items?

```{r descriptive statistics}

print(length(unique(data$run_id)))
# whatever outputs here is the number of respondents

# number of total words guessed
print(sum(data$total))

# number of words guessed correctly
print(sum(data$correct))

# number of words guessed incorrectly
print(sum(data$incorrect))

# we can also do this per participant
results_table_per_participant <- data %>%
  group_by(run_id) %>% 
  summarise(total_incorrect = sum(incorrect),
            total_correct= sum(correct),
            total_guesded = sum(total))

# we can also do this per song
results_table_per_music <- data %>%
  group_by(music) %>% 
  summarise(total_incorrect = sum(incorrect),
            total_correct= sum(correct),
            total_guesded = sum(total))

# we can also do per participant, then per music
results_table_per_participant_music <- data %>%
  group_by(run_id, music) %>% 
  summarise(total_incorrect = sum(incorrect),
            total_correct= sum(correct),
            total_guesded = sum(total))
```

## ploting

```{r plotting}

ggplot(data, aes(x=music, y=correct ))+
geom_boxplot()+
  labs(title = 'Number of correct guesses per music excerpt')

ggplot(data, aes(x=music, y=incorrect ))+
geom_boxplot()+
  labs(title = 'Number of incorrect guesses per music excerpt')

```

## Inferential statistics

This is where we want to do statistics to see if there are any significant differences between each of these four conditions.