---
title: "Example Analysis Experimental Study"
author: "Rebecca Scarratt"
date: "2023-07-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this script, we will be analysing the data that was geenrating using your group's online study.
As you did an experimental study, our aim is to find the mean difference between each group, see if this difference is statistically significant and plot the data

```{r load packages}
library(dplyr)
library(ggpubr)

library(ggplot2)

library(tidyverse)

# Set seed for reproducability
set.seed(1)

# set working directory
setwd("C:/Users/au672599/OneDrive - Aarhus Universitet/Documents/PhD Rebecca/Summer School")

```

```{r load data}
# find where you saved the downloaded file
# add that location to this script

data <- read.csv('FILELOCATION/FILENAME.csv')
data <- read.csv('example-experimental-study.csv')

# cognition.run gives you more information that you need. So the first step to any data analysis is to select the variables and rows of interest

# now we can filter on columns, to only get the informative columns that tells us what the task was and what they answered.

data <- data[c('run_id', 'stimulus', 'response','task')]

# we will be filtering the rows based on the column 'task' as that is the column that tells us the question that was asked for each row. 

data <- subset(data, task %in% c('gender', 'trial'))

data[data=="40percentslower.wav"] <- "_slow"
data[data=="40percentfaster.wav"] <- "_fast"

# Here 'response' has a strange format, so we run this code to only get the response
subset_1 = subset(data, task %in% c('gender'))
subset_1[c('Irrelevant', 'Irrelevant1', 'Irrelevant2', 'answer', 'Irrelevant4')] <- str_split_fixed(subset_1$response, '"', 5)
subset_1 <- subset_1[c("run_id", "answer", 'task')]

# because the 'task' doesn't give us information about which tempo of music was played, we have to merge it with 'stimulus'
subset_2 = subset(data, task %in% c('trial'))
colnames(subset_2)[3] <- 'answer'

subset_2 <- subset_2 %>% unite('task', task,stimulus, remove = TRUE)

data <- merge(subset_1, subset_2, by='run_id')

colnames(data) <- c('run_id', 'gender', 'remove', 'trial', 'answer')
data<- data[c('run_id', 'gender', 'trial', 'answer')]

```


Now that our data is organised well, we can look at it and answer basic descriptive questions.
In general studies, this would be looking at age, gender and maybe nationality of respondents.
We can also look at the spread of the answers to check for outliers

```{r descriptives}
# let's count how many people answered and check that they all answered the same number of questions
data %>% count(run_id)

data$gender <- as.factor(data$gender)
summary(data$gender)
# here we can see how many people chose Female-Male or Non-binary, be careful because here each particpant is counted twice

 # we make the variables be numeric
data$answer <- as.numeric(data$answer)

# we can also plot each variable to see its distribution
plot(density(data$answer))

```


```{r plot data}
trial_fast = subset(data, trial == 'trial__fast')
trial_slow = subset(data, trial == 'trial__slow')

plot(trial_fast$answer, trial_slow$answer, main="Plot trial fast vs trial slow",
   xlab="trial fast", ylab="Trial slow", pch=19)

ggplot(data, aes(x = trial, y = answer, fill = trial)) +
  stat_summary(
    fun = mean,
    geom = "bar",
    position = "dodge",
    col = "black",
    linewidth =0.5
  ) +
  scale_fill_manual(values = c("trial__fast" = "#f5f3e5", "trial__slow" = "#eed2a5"))+
  xlab("Tempo") +
  ylab("Mean Tension") +
  ggtitle("Tension by Tempo") +
  theme_bw()

# per participant
ggplot(data, aes(x = trial, y = answer, fill=trial)) +
  stat_summary(
    fun = mean,
    geom = "bar",
    position = "dodge",
    col = "black",
    linewidth =0.5
  ) +
  scale_fill_manual(values = c("trial__fast" = "#f5f3e5", "trial__slow" = "#eed2a5"))+
  xlab("Tempo") +
  ylab("Mean Tension") +
  ggtitle("Tension by Tempo") +
  theme_bw()+
  facet_wrap(~run_id)

```


```{r statistical testing}
# check assumptions
# normality
# homoskedasticity

# what to do if assumptions are met


# what to do if assumptions are not met
```

