---
title: "Example Analysis Correlation Study"
author: "Rebecca Scarratt"
date: "2023-07-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this script, we will be analysing the data that was geenrating using your group's online study.
As you did a correlational study, our aim is to find the correlation coefficient and plot the data and the correlation line

```{r load packages}
library(dplyr)
library(ggplot2)
library(ggpubr)
library(tidyverse)

# Set seed for reproducability
set.seed(1)

# set working directory
setwd("C:/Users/au672599/OneDrive - Aarhus Universitet/Documents/PhD Rebecca/Summer School")

```

```{r load data}
# find where you saved the downloaded file
# add that location to this script

data <- read.csv('FILELOCATION/FILENAME.csv')
data <- read.csv('example-correlation-study.csv')

# cognition.run gives you more information that you need. So the first step to any data analysis is to select the variables and rows of interest

# now we can filter on columns, to only get the informative columns that tells us what the task was and what they answered.

data <- data[c('run_id', 'response','task')]

# we will be filtering the rows based on the column 'task' as that is the column that tells us the question that was asked for each row. 

data <- subset(data, task %in% c('gender', 'like_pop', 'practice'))

# Here 'response' has a strange format, so we run this code to only get the response
subset_1 = subset(data, task %in% c('gender', 'practice'))
subset_2 = subset(data, task %in% c('like_pop'))
colnames(subset_2)[2] <- 'answer'

subset_1[c('Irrelevant', 'Irrelevant1', 'Irrelevant2', 'answer', 'Irrelevant4')] <- str_split_fixed(subset_1$response, '"', 5)
subset_1 <- subset_1[c("run_id", "answer", 'task')]

data <- rbind(subset_1, subset_2)

# now we need to flip how the data is represented to have each type of task in a different column
data%>%
  pivot_wider(names_from = task, values_from = answer) -> data

```

Now that our data is organised well, we can look at it and answer basic descriptive questions.
In general studies, this would be looking at age, gender and maybe nationality of respondents.

```{r descriptives}
# let's count how many people answered and check that they all answered the same number of questions
data %>% count(run_id)

data$gender <- as.factor(data$gender)
summary(data$gender)
# here we can see how many people chose Female-Male or Non-binary

 # we make the variables be numeric
data$practice <- as.numeric(data$practice)
data$like_pop <- as.numeric(data$like_pop)

# we can also plot each variable to see its distribution
plot(density(data$practice))

plot(density(data$like_pop))
```


```{r plot data}

plot(data$like_pop, data$practice, main="Plot of the number of hours listened to per week as a function of pop music liking",
   xlab="Pop liking ", ylab="Numbers of hours of music listened to", pch=19)

# plot with Pearson correlation coefficient
ggplot(data, aes( x=like_pop, y=practice ))+
geom_point()+
stat_cor(method = "pearson", label.x = -5, label.y = 30)+
geom_smooth(method="lm", se=FALSE)

# plot with Spearman correlation coefficient
ggplot(data, aes( x=like_pop, y=practice ))+
geom_point()+
stat_cor(method = "spearman", label.x = -5, label.y = 30)

```

```{r plot data taking gender into account}

# plot with Pearson correlation coefficient
ggplot(data, aes( x=like_pop, y=practice ))+
geom_point()+
stat_cor(method = "pearson", label.x = -5, label.y = 30)+
geom_smooth(method="lm", se=FALSE)+
facet_wrap(~gender)

# plot with Spearman correlation coefficient
ggplot(data, aes( x=like_pop, y=practice ))+
geom_point()+
stat_cor(method = "spearman", label.x = -5, label.y = 30)+
facet_wrap(~gender)
```

