---
title: "Preprocessing Script for Summer School"
author: "Rebecca Scarratt"
date: "2023-07-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
## Introduction

This is a script that will transform your data file from a mess of rows and columns that don't make any sense to a structure dataset.

in every R script, we start by loading the packages we will be using, defining the working directory and loading in the data. Make sure that the data file in the working directory. The working directory is the only folder that R can see when running this script , so it's important that all the files you will need are in that folder. It's also where the output files will save.

```{r load packages, working directory and data}
# we load the packages
library(dplyr)
library(ggplot2)
library(tidyverse)

# Set seed for reproducability
set.seed(1)

# set working directory
setwd("C:/Users/au672599/OneDrive - Aarhus Universitet/Documents/PhD Rebecca/Summer School/Online studies data")

# load in the data file. Note this only works with a .csv file. Here you need to change the name of the file.

data <- read.csv('survey_results_group1.csv')

# if it worked correctly, you should now see the dataframe 'data' appear in the Environment panel. You can click on it, to open it and check that it looks like your messy data file.
```

## Data reducing

Now that the data is loaded, we can start removing columns and rows that we don't need and making what we do need be more intuitive.
Of course, we don't change anything of what the cells contain, so it's important to check that we don't remove too much that would modify the data.
How exactly to do this step depends on the experiment.

```{r removing rows and columns}
# first, let's remove the rows we don't want. In the trial_type column, it tells us what type of question/display we had. It saves information for all of them, but we are not always interested in all of them. This depends on each experiment but in your case, you are only interested in 'survey-multi-choice' as that's where participants responses are stored. The rest can go. We will add in the audio information later as it's not randomised

data <- subset(data, trial_type %in% c('survey-multi-select'))

# we want to keep columns 'run_id and response'. The rest we can remove as it doesn't tell us anything important.

data<- data[c('run_id', 'response')]

# now you can open data again to make sure you kept and deleted the right things. If there is a mistake, you can always load the data again and start again.

```

## Data reorganisation

Now that we have less rows and columns to deal with, we can make them be more intuitive.
At this point, it is sometimes helpful to draw out what type of table/dataframe you would want your data to look like in the end, and then work step by step to that goal.

```{r formating}
# let's deal with the response column first. This is probably not the most elegant way to do this, but it works :p

data[c('1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11', '12', '13', '14', '15', '16', '17', '18', '19', '20', '21', '22', '23', '24', '25', '26', '27', '28', '29', '30', '31', '32', '33', '34', '35', '36', '37', '38', '39', '40', '41', '42', '43')] <- str_split_fixed(data$response, '"', 43)

data <- data[c('run_id', '4', '6', '8', '10', '12', '14', '16', '18', '20', '22', '24', '26', '28', '30', '32', '34', '36', '38', '40', '42')]

# this is combining the many columns into one column
combine_columns_to_string <- function(row) {
  values <- row[-c(1)]  # Skip the first column (ID) and extract values
  values[values == ""] <- NA  # Convert empty values to NA
  values <- na.omit(values)  # Remove missing values
  if (length(values) > 0) {
    values_string <- paste(values, collapse = ", ")  # Combine into a single string
  } else {
    values_string <- NA_character_  # Set to NA if there are no non-missing values
  }
  return(values_string)
}

data <- data %>%
  mutate(selected_response = apply(data, 1, combine_columns_to_string))

data <- data[c('run_id','selected_response')]

# so our response column is now readable. Now we need to add the audio track information. Because there was no randomisation, we can do this quite easily.
# However, first we need to remove any participant that didn't complete the survey.

# removing non-complete participants

data %>% count(run_id)
# as you can see in the output of this, every participant should have 8 rows associated with it (for now it's 4 because there are four conditions).

# here you can remove all the run_ids of participants who have less than 4 'counts'/rows.

data <- subset(data, !(run_id %in% c('17', '18')))

# we can do the above comand again to check we now have removed the non-completing participants

data %>% count(run_id)

# Now we can continue
  
audio_vector <- c('classical_1', 'metal_1', 'metal_2', 'classical_2')

# Repeat the vector to create a new data frame. Here you need to change the number of times the list of audio stimuli is repeated so that it matches the length of data. So if it is 60, we calculate 60/4=15, so we repeat it 15 times.
audio_info <- data.frame(strings = rep(audio_vector, times = 15))

# we can now add the audio infromation to the response information

data <- cbind(data, audio_info)

# check that everything matches up before proceeding
```

## Specifics for this data
In your specific experiment, you want to add a see how many of the items they selected were correct and how many were incorrect. So we need to add two columns to the dataframes (items_correct, items_incorrect) that will include the number of correct and incorrect items.

First we need to have saved for each music piece (as the music coresponded with the images), which are correct items.

```{r correct/incorrect responses}

correct_items_1 <- c('Courgette', 'Potato', 'Bread', 'Fries', 'Cucumber', 'Aubergine', 'Bell pepper','Tomato', 'Strawberry', 'Crisps', 'Lemon', 'Donut', 'Apple', 'Pommegranate', 'Salmon', 'Orange', 'Croissant', 'Raspberry')

correct_items_2 <- c('Moon', 'Volcano', 'Boat', 'Rainbow', 'Lion', 'Elephant', 'Clownfish', 'Flower', 'Butterfly', 'Tree', 'Parrot', 'Ant', 'Fire', 'Bee', 'Dolphin', 'Polar bear', 'Helicopter', 'Thunder')

correct_items_3 <- c('Heart', 'Blood', 'Injury', 'Gloves', 'Hospital', 'Stethoscope', 'Lab coat', 'Coffee', 'Virus', 'Wheelchair', 'Muscle', 'Vaccin', 'Scissors', 'Alcohol', 'Brain', 'Medication', 'Liver', 'Bone')

correct_items_4 <- c('Bed', 'Mixer', 'Plate', 'Cutlery', 'Desk', 'Pan', 'Blanket', 'Lamp', 'Pot', 'Toilet paper', 'Curtains', 'Mirror', 'Sink', 'Glass', 'Bottle', 'Tupperware', 'Pillow', 'Spatula')
# I don't think Tupperware was in the list they cold select from and Toilet paper also wasn't. So check and edit this if necessary

#Now let's count how many are in each response row

count_correct_incorrect_words <- function(response, correct_items) {
  words <- strsplit(response, " ")[[1]]  # Split response into words
  correct_words <- sum(words %in% correct_items)  # Count correct words
  incorrect_words <- sum(!words %in% correct_items)  # Count incorrect words
  return(list(correct = correct_words, incorrect = incorrect_words))
}

# let's do it seperately per image

items_1 <- subset(data, strings == 'classical_1')

count_matching_items <- function(cell, vector) {
  items <- unlist(strsplit(cell, ",\\s*"))  # Split cell into individual items
  num_matches <- sum(items %in% vector)  # Count matches with 'my_vector'
  num_non_matches <- sum(!items %in% vector)  # Count non-matches with 'my_vector'
  return(list(matches = num_matches, non_matches = num_non_matches))
}

# Apply the function to the 'column_name' column and create new columns for the counts
items_1 <- items_1 %>%
  rowwise() %>%
  mutate(counts = list(count_matching_items(selected_response, vector = correct_items_1)))

# Unpack the list of counts into separate columns
items_1 <- items_1 %>%
  mutate(num_matches = counts$matches, num_non_matches = counts$non_matches) %>%
  select(-counts)


# for image 2

items_2 <- subset(data, strings == 'metal_1')

# Apply the function to the 'column_name' column and create new columns for the counts
items_2 <- items_2 %>%
  rowwise() %>%
  mutate(counts = list(count_matching_items(selected_response, vector = correct_items_2)))

# Unpack the list of counts into separate columns
items_2 <- items_2 %>%
  mutate(num_matches = counts$matches, num_non_matches = counts$non_matches) %>%
  select(-counts)



# for image 3

items_3 <- subset(data, strings == 'metal_2')

# Apply the function to the 'column_name' column and create new columns for the counts
items_3 <- items_3 %>%
  rowwise() %>%
  mutate(counts = list(count_matching_items(selected_response, vector = correct_items_3)))

# Unpack the list of counts into separate columns
items_3 <- items_3 %>%
  mutate(num_matches = counts$matches, num_non_matches = counts$non_matches) %>%
  select(-counts)



# for image 4

items_4 <- subset(data, strings == 'classical_2')

# Apply the function to the 'column_name' column and create new columns for the counts
items_4 <- items_4 %>%
  rowwise() %>%
  mutate(counts = list(count_matching_items(selected_response, vector = correct_items_4)))

# Unpack the list of counts into separate columns
items_4 <- items_4 %>%
  mutate(num_matches = counts$matches, num_non_matches = counts$non_matches) %>%
  select(-counts)


# now merge them all back to the main dataframe

data <- rbind(items_1, items_2, items_3, items_4)

data$total_answers <- data$num_matches + data$num_non_matches

# let's rename some columns for better understanding

colnames(data) <- c('run_id','response','music', 'correct', 'incorrect', 'total')

# now we have finished the pre-processing of the data, we can save this final dataframe so we can continue the analyses and now have to always redo every preprocessing step

write.csv(data, 'survey_data_group1.csv')
```




